V1298~Tau with TESS: Updated Ephemerides, Radii, and Period Constraints from a Second Transit of V1298~Tau~e

### 2021-11-11 src/ms.tex
final edits

We modeled the background within out GP. We defined a quadratic trend with respect to time for varying the background flux, where each polynomial coefficient was drawn from a normal distribution. Then, we generated a Vandermonde matrix ($A$) of time. This is a way of introducing a polynomial least-squares regression with respect to time. The final background flux was calculated by taking $bkg = A \cdot trend$.

@@

\subsection{Constraining \planete's Period}
\sname (EPIC~210818897) was observed during Campaign 4 of the \textit{K2} mission. There was a single transit of \planete in the original \textit{K2} data, which occurred roughly in the middle of the campaign. Since no other transits were detected, this provides a lower period limit of 36~days. Using the original transit timing from \textit{K2} and this new transit timing from \tess, we developed a new method for constraining the period of \planete. For this analysis, we used the \texttt{EVEREST 2.0} \citep{luger18} version of the \textit{K2} light curve.

@@

We ran 5 chains with 500 tuning steps and 5000 draws. We discarded the tuning steps before our analysis. Our results are presented in Figure~\ref{fig:period_e}, where we plot the median period for each tested harmonic against the posterior probability of each harmonic.

@@

A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \citep{wang19}, while transits in the optical probe lower atmospheric pressures, resulting in larger transit depths \citep{gao20}. Therefore, the difference in transit depths could be due to the difference in bandpass wavelength coverage between \textit{Kepler} \citep[400-900~nm;][]{Howell2014} and \tess\ \citep[600-1000~nm][]{Ricker2015}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{figure}[!b]
\begin{center}
\includegraphics[width=0.465\textwidth,trim={0.25cm 0 0 0}]{figures/folded_compare.pdf}
\caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the original \textit{K2} data (black). The residuals between the \tess\ data and each fit are shown underneath. A comparison of measured $R_p/R_\star$ are presented at the bottom, with a 1-to-1 line plotted in black for reference. The transit depths for \planetknown are shallower in the new \tess\ data, while the transit depth for \planete is deeper. We speculate the variation in transit depths could be due to starspot crossing events.} \label{fig:compare}
\end{center}
\end{figure}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The ability of a planet to retain hazes/transition hazes is negatively correlated with its equilibrium temperature, $T_{eq}$, internal temperature $T_{int}$, and positively correlated with mass, $M_{core}$. \allplanets have calculated $T_{eq} < 1000$\,K, assuming an albedo = 0 \citep{David2019a}. Young planets are believed to have high $T_{int}$ due to ongoing gravitational contraction \citep{gu04}. The combination of these two parameters make these planets more likely to host extended high-altitude hazes in their atmospheres, while outflow winds lead to the formation of transition hazes \citep{gao20}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{figure}[!t]
\begin{center}
\includegraphics[width=0.465\textwidth,trim={0.25cm 0 0 0}]{static/dilution.pdf}
\caption{The change in $R_p/R_\star$ as a function of pixel for \planetb (top) and \planete (bottom) overlaid with a sky image of \sname taken with the Digitized Sky Survey (DSS) r-band. \sname is highlighted by the white circle; nearby sources with \tess\ magnitudes $T_\textrm{mag} < 14$ are marked with blue x's.} \label{fig:dilution}
\end{center}
\end{figure}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Radius of \planete}

@@

$T_0$ [BKJD - 2454833] & $4648.1576_{-0.0036}^{+0.0040}$ & $4645.4158^{+0.0024}_{-0.0028}$& $4648.0927_{-0.0017}^{+0.0015}$ & $4648.8002 \pm0.0014$\\
P [days]               & $8.2481_{-0.0022}^{+0.0018}$ & $12.4007_{-0.0020}^{+0.0023}$ & $24.1371_{-0.0021}^{+0.0022}$ & $50.29 \pm 6.62$ \\

@@

%\iffalse

>>>>

We modeled the background within our GP. We defined a quadratic trend with respect to time for varying the background flux, where each polynomial coefficient was drawn from a normal distribution. Then, we generated a Vandermonde matrix ($A$) of time. This is a way of introducing a polynomial least-squares regression with respect to time. The final background flux was calculated by taking $bkg = A \cdot trend$.

@@

\subsection{Constraining \planete's Period}

\sname (EPIC~210818897) was observed during Campaign 4 of the \textit{K2} mission. There was a single transit of \planete in the original \textit{K2} data, which occurred roughly in the middle of the campaign. Since no other transits were detected, this provides a lower period limit of 36~days. Using the original transit timing from \textit{K2} and this new transit timing from \tess, we developed a new method for constraining the period of \planete. For this analysis, we used the \texttt{EVEREST 2.0} \citep{luger18} version of the \textit{K2} light curve.

@@

We ran 3 chains with 500 tuning steps and 5000 draws. We discarded the tuning steps before our analysis. Our results are presented in Figure~\ref{fig:period_e}, where we plot the median period for each tested harmonic against the posterior probability of each harmonic.

@@

A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \citep{wang19}, while transits in the optical probe lower atmospheric pressures, resulting in larger transit depths \citep{gao20}. Therefore, the difference in transit depths could be due to the difference in bandpass wavelength coverage between \textit{Kepler} \citep[400-900~nm;][]{Howell2014} and \tess\ \citep[600-1000~nm;][]{Ricker2015}.

The ability of a planet to retain hazes/transition hazes is negatively correlated with its equilibrium temperature, $T_{eq}$, internal temperature $T_{int}$, and positively correlated with mass, $M_{core}$. \allplanets have calculated $T_{eq} < 1000$\,K, assuming an albedo~=~0 \citep{David2019a}. Young planets are believed to have high $T_{int}$ due to ongoing gravitational contraction \citep{gu04}. The combination of these two parameters make these planets more likely to host extended high-altitude hazes in their atmospheres, while outflow winds lead to the formation of transition hazes \citep{gao20}.

@@

\subsection{Radius of \planete}

@@

$T_0$ [BKJD - 2454833] & $4648.1576_{-0.0034}^{+0.0042}$ & $4645.4113_{-0.0021}^{+0.0023}$ & $4648.0913_{-0.0013}^{+0.0015}$ & $4648.7975_{-0.0014}^{+0.0012}$ \\
P [days]               & $8.2479_{-0.0019}^{+0.0016}$ & $12.4030_{-0.0016}^{+0.0020}$ & $24.1382_{-0.0022}^{+0.0019}$ & $50.29 \pm 6.62$ \\

@@
